\begin{itemize}
\tightlist
\item
  First an foremost, we need to collect required data and datasets
  including journey metro transaction datasets, user profile datasets,
  station datasets, fare structure, user profile, security maintenance
  record, etc
\item
  Further data collection from user perspective and feedback is in order
  to maintain the user satisfaction and requirements.
\item
  Then we start analysis the data and afterwards filter out the data for
  advance to the system development.
\item
  A central server is development using the data we gather for overall
  data communication.
\item
  The Central server talks to the metro rail system, server operation \&
  information system, system accounts, user management and the GUI
  application which is for user profile management and balance
  monitoring.
\item
  The user management system issue card checking for new valid user and
  proceed with existing user verifying fraudulent in the system. User
  authentication and authorization are need to be build strictly.
\item
  The fraudulent detection is monitored using pattern matching, anomaly
  detection, behavioral analysis, recognizing the machine learning
  models and IP address tracking.
\item
  Develop API and transaction gateway to handle various transaction
  operation such as loading funds onto smart card and deduction fare.
  Calculation of fare need to be done based on the predefined fare
  structure and the distance it covers.
\item
  Develop GUI using fronted framework to monitor and track the whole
  user account and balance online remotely.
\item
  Integrate back-end, database and frontend maintain necessary security
  measurement.
\item
  Test the smart card on-premises.
\end{itemize}
